## Fit the growth mixture model in Mplus

This code fits a four class growth mixture model.  The model assumes a linear trajectory with equally spaced time intervals.
```{r}
gmm.model.1 <- " %OVERALL% 
                 i s | y1@0 y2@1 y3@2 y4@3 y5@4 y6@5 ;
               "
gmm.body <- mplusObject(
  ANALYSIS = "type=mixture; starts = 100 20;",
  VARIABLE = "classes = c(4); idvariable = id;",
  MODEL = gmm.model.1,
  OUTPUT = "",
  SAVEDATA = "save = cprob; file=model1prob.dat;",
  usevariables = c("id", "y1", "y2", "y3", "y4", "y5", "y6"),
  rdata = data
)
gmm.fit <- mplusModeler(gmm.body, modelout = "gmm001.inp", run = TRUE)

```

## Read in the saved class membership and parameter estimates

After fitting the model in Mplus, we need to get the results back into R.

This code reads in and saves the parameter estimates to an object called *param1*.

```{r}

param1 <- extractModelParameters("gmm001.out")$unstandardized %>% 
  filter(grepl("Means", paramHeader)) %>%
  filter(!grepl("Categorical.Latent.Variables", LatentClass))
```

This code reads in the predicted class membership and merges it with the original data. It also recreates the "long" format of the data.

```{r}
foo <- getSavedata_Data("gmm001.out") %>%
  rename(model1.c = C) %>%
  select(ID, model1.c) 
colnames(foo) <- tolower(names(foo)) 

data <- data %>%
  full_join(foo, by= "id" )

data.long <- data %>% 
  gather(foo, y, y1:y6) %>%
  mutate(time = as.numeric(str_sub(foo, 2))) %>%
  arrange(id, time) %>%
  select(-foo)
```
